Categorical Data Analysis
========================================================
author: Hiroki Matsui
date: 2015/1/21

本日お話する内容
=======================================================
- Categorical Outcome in Rheumatoid Arthritis (2min)
- Categorical Outcome の解析（単変量） (5min)
- Categorical Outcome の解析（多変量） (8min)
- 注意事項 (10min)
- 参考資料 (-min)




Categorical data
========================================================
- アウトカムとなる変数が二値以上の離散的な値であること
- Familiar with
 - Death (1 = death)
 - Readmission (1 = readmission)
- In Rheumatoid Arthritis
 - DAS remission (DAS28-ESR < 2.6)
 - HAQ remission (HAQ-DI <0.5)
 - Radiographic remission (delta TSS ≤0)



Analysing categorical data (single variable)
========================================================
- 連続変数の場合
 - 平均値を比較する。
 - t-testやANOVA  等でグループ間の平均を比較することが一般的
- カテゴリカル変数の場合
 - 割合(population)を比較する。
 - $\chi^2$ test 等でグループ間の割合の比較をするのが一般的

Statistical testing for categorical data (single variable)
========================================================
- $\chi^2$ test with R
 - chisq.test(x)
```{r}
 x <- matrix(c(14, 8, 4, 17), ncol=2, byrow=T)
 print(x)
 chisq.test(x)
```
 - Fisher's exact test
  - fisher.test(x)
```{r }
 fisher.test(x)
```
  
Analysing categorical data (single variable)  
========================================================
- 割合の比較
 - リスク差
 - リスク比
 - オッズ比
 
```{r, echo=FALSE}
plot(cars)
```
